PTFO 8-8695: Two Stars, Two Signals, No Planet

### 2020-05-01 paper/ms.tex
fix typo

% PENDING
\author[0000-0001-6588-9574]{K. A. Collins} % karenacollins@outlook.com
\affiliation{Center for Astrophysics \textbar \ Harvard \&
Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}

@@

We also used the Gaia data to see if the observed luminosity of \ptfo
is too bright to be a single star, i.e., if it is a ``photometric
binary.'' To assemble a set of stars coeval with \ptfo, we used the
25$\,$Ori-1 members identified by \citet{kounkel_apogee2_2018}, and
discussed in Section~\ref{subsec:hierarchical}.

>>>>

%CONFIRMED
\author[0000-0001-6588-9574]{K. A. Collins} % karenacollins@outlook.com
\affiliation{Center for Astrophysics \textbar \ Harvard \&
Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}

@@

We also used the Gaia data to see if the observed luminosity of \ptfo\ 
is too bright to be a single star, i.e., if it is a ``photometric
binary.'' To assemble a set of stars coeval with \ptfo, we used the
25$\,$Ori-1 members identified by \citet{kounkel_apogee2_2018}, and
discussed in Section~\ref{subsec:hierarchical}.
